Behavior Driven Development in Haskell

### 2012-05-27 paper.tex
Add a comment
Fix typo
Add some text to "Combinators for expectations"

        \begin{verbatim}
expect {launche_missiles}.to raise_error
        \end{verbatim}

@@

\subsection{Combinators for expectations}
We propose to use three combinators to set expectations about the
outcome of code examples.

\begin{quote}\small\begin{verbatim}
shouldBe :: (Show a, Eq a) => a -> a -> Assertion
shouldSatisfy :: Show a => a -> (a -> Bool) -> Assertion
shouldReturn :: (Show a, Eq a) => IO a -> a -> Assertion
\end{verbatim}\end{quote}

@@

>>>>

        \begin{verbatim}
expect {launch_missiles}.to raise_error
        \end{verbatim}

@@

\subsection{Combinators for expectations}

We propose four combinators, that can be used to set expectations
about the outcome of code examples.

A common expectation is, that a value should be equal to an other
value.

\begin{quote}\small\begin{verbatim}
x `shouldBe` 23
\end{verbatim}\end{quote}

\noindent This is just an other name for HUnit's \texttt{@?=}
operator.  The type is:

\begin{quote}\small\begin{verbatim}
shouldBe :: (Show a, Eq a) => a -> a -> Assertion
\end{verbatim}\end{quote}

\noindent Or we may expect that a value satisfies some predicate.

\begin{quote}\small\begin{verbatim}
x `shouldSatisfy` (< 23)
\end{verbatim}\end{quote}

\noindent The value is required to be in the \texttt{Show} class, so that a
useful error message can be given when the predicate is not satisfied.

\begin{quote}\small\begin{verbatim}
shouldSatisfy :: Show a => a -> (a -> Bool)
  -> Assertion
\end{verbatim}\end{quote}

\noindent Examples are often used to provide evidence for {\tt IO}
actions.

\begin{quote}\small\begin{verbatim}
launchMissiles >>=
  (`shouldBe` (Left "not implemented"))
\end{verbatim}\end{quote}

\noindent So we propose a shortcut for this common use case.

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldReturn` (Left "not implemented")
\end{verbatim}\end{quote}

\begin{quote}\small\begin{verbatim}
shouldReturn :: (Show a, Eq a) => IO a -> a
  -> Assertion
\end{verbatim}\end{quote}

\subsubsection{Expecting exceptions}

HUnit does not provide any versatile mechanism to expect that an
exception is thrown.  So we propose a combinator for that.

\begin{quote}\small\begin{verbatim}
shouldThrow :: Exception e => IO a -> (e -> Bool)
  -> Assertion
\end{verbatim}\end{quote}

\noindent It takes an {\tt IO} action, and a predicate.  The predicate
servers two purposes.  It selects the type of the expected exception,
and constraints the value.

\begin{quote}\small\begin{verbatim}
launchMissiles `shouldThrow` (== ExitFailure 1)
\end{verbatim}\end{quote}

\noindent To make it more convenient, to expect any exception of a
certain type, we provide type-restricted versions of {\tt (const
True)} for all standard exceptions.

\begin{quote}\small\begin{verbatim}
anyArithException :: ArithException -> Bool
anyArithException = const True
\end{verbatim}\end{quote}

\noindent Which can be used like so:

\begin{quote}\small\begin{verbatim}
let x = 1 `div` 0 in (x `seq` return x)
      `shouldThrow` anyArithException
\end{verbatim}\end{quote}

@@

\begin{quote}
@kazu: Can we use \verb|reverse| instead of \verb|rev| here?
\end{quote}
